\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{ifthen}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\newcommand{\resumeheader}[6]{%
    \begin{center}
        {\Large \textbf{#1}}\\[4pt]
        \href{mailto:#2}{#2} $|$ 
        \href{#3}{Portfolio} $|$ 
        \href{#4}{Github} $|$ 
        \href{#5}{LinkedIn} $|$ 
        #6
    \end{center}
}

\newcommand{\education}[4]{%
    \textbf{#1}, #2\ (#3) \hfill #4
}

\newcommand{\experience}[4]{%
    \textbf{#1,} #2 -- #3 \hfill #4
}

\newcommand{\project}[3]{%
    \textbf{#1}%
    \ifthenelse{\equal{#2}{}}{}{ \href{#2}{Github}}%
    \ifthenelse{\equal{#3}{}}{}{ \,|\, \href{#3}{Live}}%
}

\begin{document}

\resumeheader{Shobhnik}
{shobhnikw@gmail.com}
{https://shobhnik.xyz}
{https://github.com/shobhnik13}
{https://www.linkedin.com/in/shobhnik13/}
{+91-8906044442 | Noida, India}

\section{Education}
\education{Maharaja Agrasen Institute of Technology}{B.Tech in IT}{8.9 CGPA}{Dec 2021 -- Feb 2025}

\section{Experience}

\experience{Backend Engineer}{Xane AI}{Gurugram, India}{Jan 2026 -- Present}
\begin{itemize}

\item Designing end to end \textbf{HLD and LLD architectures} for multiple production-grade microservices using \textbf{Node.js, Bun, TypeScript, PostgreSQL Knex and AWS}, designing database schemas, inter service communication, and scalability strategies.

\item Built a high throughput \textbf{data ingestion pipeline} that parses large scale PDF documents using \textbf{OCR techniques}, validates and transforms structured/unstructured data, and ingests \textbf{millions of records} into PostgreSQL with optimized batching and indexing.

\item Developed a fully production ready \textbf{AI agent} using \textbf{Deep Agents and LangChain} to analyze datasets and predict key operational outcomes, reducing manual processing time from \textbf{48 hours to under 3 hours}.

\end{itemize}
\vspace{1mm}

\experience{Software Engineer}{Otomashen (E-solutions)}{Noida, India}{Feb 2025 -- Jan 2026}
\begin{itemize}

\item Built and scaled a high-throughput \textbf{EDI/X12 processing engine} handling 20k+ claim files and millions of encrypted denial records, driving a \textbf{166\% revenue increase}.

\item Optimized backend services in \textbf{Node.js/TypeScript} with query tuning, indexing, and caching; reduced API latency from \textbf{10s to <1s} at scale.

\item Engineered a \textbf{real-time dispatch system} for proximity based doctor matching, request lifecycle (accept/decline), and instant notifications.

\item Delivered \textbf{4 production grade client systems}, led one end to end as \textbf{Lead Developer}, owning architecture and execution.

\end{itemize}

\vspace{1mm}

\experience{Full Stack Developer}{Stealth Startup}{Remote}{Aug 2024 -- Jan 2025}
\begin{itemize}[leftmargin=20pt, topsep=0pt, itemsep=2pt]

\item Owned the product end to end as the sole engineer, building all frontend workflows and integrating backend APIs from design to production.

\item Architected the complete backend system, designing scalable architecture, database schema, and core processing workflows.

\item Built a high-throughput notification pipeline using \textbf{Node.js/TypeScript, BullMQ, Redis, PostgreSQL, and Socket.io}, delivering thousands of notifications per second, implemented vector search for fast large scale retrieval.

\item Developed a production grade AI agent using \textbf{LangGraph, LangChain, and Gemini} for complex workflow automation.

\item Scaled the platform to \textbf{200--250 active users} managing \textbf{500k+ production records} in production.

\end{itemize}

\section{Projects}

\project{InsightPlus}{https://github.com/Shobhnik13/InsightPlus}{}
\begin{itemize}[leftmargin=15pt, topsep=0pt, itemsep=2pt]

    \item Built a fully open-source, self-hostable and easy-to-integrate analytics engine using NestJS, TypeScript, and Redis Streams, ingesting \textbf{tens of thousands of events/sec} via simple API calls.

    \item Designed a dual-database architecture supporting \textbf{PostgreSQL and ClickHouse} for metrics like MAU, DAU, retention, and custom events.

\end{itemize}

\section{Technical Skills}
\textbf{Languages:} Javascript, Typescript, Golang(Go)

\textbf{Frameworks:} Next.js, NestJS, React.js, Node.js, Express.js, Langchain, Deep agents

\textbf{Coursework:} System Design (HLD \& LLD), Computer Networks, Operating Systems, DBMS

\textbf{DevOps/Infra:} Microsoft Azure, AWS, Vercel, Git, Docker, CI/CD, BullMQ, Burp Suite

\textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis, ClickHouse

% \section{Achievements}
% \textbf{•} Top 3 in HackJNU and HackIIITD \quad
% \textbf{•} Solved 500+ DSA problems \quad
% \textbf{•} Led a team of 5+ developers \quad
% \textbf{•} Co-founded a travel agency serving 2,000+ customers

\end{document}